\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-01-17 paper/fse23/tables/test-results-hs-all-numbers.tex
modify table

\DefMacro{test-results-hs-model0-lc2-num-all-fail}{3,220}
\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{98.66}
\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{98.65}
\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{18}
\DefMacro{test-results-hs-lc18}{Denouncements of hate that quote it}
\DefMacro{test-results-hs-lc18-num-seeds}{45,616}
\DefMacro{test-results-hs-lc18-num-exps}{300,704}
\DefMacro{test-results-hs-model0-lc18-num-all-fail}{48,804}
\DefMacro{test-results-hs-model0-lc18-num-seed-failrate}{13.78}
\DefMacro{test-results-hs-model0-lc18-num-exp-failrate}{14.14}
\DefMacro{test-results-hs-model0-lc18-num-all-failrate}{14.09}
\DefMacro{test-results-hs-model0-lc18-num-pass-to-fail}{4,831}

@@

\DefMacro{test-results-hs-model0-lc1-num-all-fail}{3,067}
\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{98.99}
\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{98.97}
\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{23}

@@

\DefMacro{test-results-hs-model0-lc4-num-all-fail}{2,770}
\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{97.74}
\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{98.18}
\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{98.16}
\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{9}

@@

\DefMacro{test-results-hs-model0-lc0-num-all-fail}{920}
\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{98.12}
\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{97.98}
\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{22}

@@

\DefMacro{test-results-hs-model0-lc10-num-all-fail}{49,929}
\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{60.60}
\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{95.07}
\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{87.81}
\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{1,169}

@@

\DefMacro{test-results-hs-model0-lc11-num-all-fail}{47,294}
\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{58.92}
\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{93.94}
\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{86.29}
\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{1,726}

@@

\DefMacro{test-results-hs-model0-lc12-num-all-fail}{145,761}
\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{97.03}
\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{97.11}
\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{2,290}

@@

\DefMacro{test-results-hs-model0-lc8-num-all-fail}{50,158}
\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{97.34}
\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{97.23}
\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{97.23}
\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{164}

@@

\DefMacro{test-results-hs-model0-lc6-num-all-fail}{17,597}
\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{97.10}
\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{70}
\DefMacro{test-results-hs-lc15}{Hate phrased as a opinion}
\DefMacro{test-results-hs-lc15-num-seeds}{22,808}
\DefMacro{test-results-hs-lc15-num-exps}{160,927}
\DefMacro{test-results-hs-model0-lc15-num-all-fail}{178,058}
\DefMacro{test-results-hs-model0-lc15-num-seed-failrate}{97.25}
\DefMacro{test-results-hs-model0-lc15-num-exp-failrate}{96.86}
\DefMacro{test-results-hs-model0-lc15-num-all-failrate}{96.91}
\DefMacro{test-results-hs-model0-lc15-num-pass-to-fail}{3,078}
\DefMacro{test-results-hs-lc14}{Hate phrased as a question}
\DefMacro{test-results-hs-lc14-num-seeds}{22,808}
\DefMacro{test-results-hs-lc14-num-exps}{185,267}
\DefMacro{test-results-hs-model0-lc14-num-all-fail}{202,023}
\DefMacro{test-results-hs-model0-lc14-num-seed-failrate}{97.37}
\DefMacro{test-results-hs-model0-lc14-num-exp-failrate}{97.06}
\DefMacro{test-results-hs-model0-lc14-num-all-failrate}{97.09}
\DefMacro{test-results-hs-model0-lc14-num-pass-to-fail}{2,956}

@@

\DefMacro{test-results-hs-model0-lc3-num-all-fail}{5,730}
\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{97.86}
\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{98.75}
\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{98.73}
\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{30}
\DefMacro{test-results-hs-lc16}{Neutral statements using protected group identifiers}
\DefMacro{test-results-hs-lc16-num-seeds}{5}
\DefMacro{test-results-hs-lc16-num-exps}{9}
\DefMacro{test-results-hs-model0-lc16-num-all-fail}{1}
\DefMacro{test-results-hs-model0-lc16-num-seed-failrate}{20.00}
\DefMacro{test-results-hs-model0-lc16-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc16-num-all-failrate}{7.14}
\DefMacro{test-results-hs-model0-lc16-num-pass-to-fail}{0}

@@

\DefMacro{test-results-hs-model0-lc9-num-all-fail}{11,939}
\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{71.04}
\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{72.59}
\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{72.52}
\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{75}
\DefMacro{test-results-hs-lc13}{Non-hate expressed using negated hateful statement}
\DefMacro{test-results-hs-lc13-num-seeds}{34,212}
\DefMacro{test-results-hs-lc13-num-exps}{243,739}
\DefMacro{test-results-hs-model0-lc13-num-all-fail}{77,191}
\DefMacro{test-results-hs-model0-lc13-num-seed-failrate}{26.90}
\DefMacro{test-results-hs-model0-lc13-num-exp-failrate}{27.89}
\DefMacro{test-results-hs-model0-lc13-num-all-failrate}{27.77}
\DefMacro{test-results-hs-model0-lc13-num-pass-to-fail}{5,222}

@@

\DefMacro{test-results-hs-model0-lc7-num-all-fail}{2,739}
\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{30.89}
\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{33.21}
\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{33.10}
\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{44}
\DefMacro{test-results-hs-lc17}{Positive statements using protected group identifiers}
\DefMacro{test-results-hs-lc17-num-seeds}{41}
\DefMacro{test-results-hs-lc17-num-exps}{182}
\DefMacro{test-results-hs-model0-lc17-num-all-fail}{14}
\DefMacro{test-results-hs-model0-lc17-num-seed-failrate}{4.88}
\DefMacro{test-results-hs-model0-lc17-num-exp-failrate}{6.59}
\DefMacro{test-results-hs-model0-lc17-num-all-failrate}{6.28}
\DefMacro{test-results-hs-model0-lc17-num-pass-to-fail}{1}

@@

\DefMacro{test-results-hs-model0-lc5-num-all-fail}{4,261}
\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{99.29}
\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{99.02}
\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{99.02}
\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{1}
\DefMacro{test-results-hs-model1-lc2-num-all-fail}{87}
\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{2.78}
\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{2.67}
\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{31}
\DefMacro{test-results-hs-model1-lc18-num-all-fail}{346,320}
\DefMacro{test-results-hs-model1-lc18-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc18-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc1-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc4-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{0.00}

@@

\DefMacro{test-results-hs-model1-lc0-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc10-num-all-fail}{5,984}
\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{10.52}
\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc11-num-all-fail}{5,984}
\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{10.92}
\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc12-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc8-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc6-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc15-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc15-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc15-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc14-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc14-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc14-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc3-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc16-num-all-fail}{14}
\DefMacro{test-results-hs-model1-lc16-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc16-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc9-num-all-fail}{16,462}
\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc13-num-all-fail}{277,951}
\DefMacro{test-results-hs-model1-lc13-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc13-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc13-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc13-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc7-num-all-fail}{8,276}
\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc17-num-all-fail}{223}
\DefMacro{test-results-hs-model1-lc17-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc17-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc17-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc17-num-pass-to-fail}{0}
\DefMacro{test-results-hs-model1-lc5-num-all-fail}{0}
\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{0}

>>>>

\DefMacro{test-results-hs-bl-lc2-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc2-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc2-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc2-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc2-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc2-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc2-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc2-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc1-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc1-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc1-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc1-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc1-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc1-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc1-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc1-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc4-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc4-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc4-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc4-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc4-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc4-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc4-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc0-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc0-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc0-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc0-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc0-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc0-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc0-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc10-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc10-num-all-fail}{5,984}
\DefMacro{test-results-hs-model0-lc10-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model0-lc10-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc10-num-all-failrate}{10.52}
\DefMacro{test-results-hs-model0-lc10-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc10-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc10-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc11-num-tcs}{133}
\DefMacro{test-results-hs-model0-lc11-num-all-fail}{5,984}
\DefMacro{test-results-hs-model0-lc11-num-seed-failrate}{50.00}
\DefMacro{test-results-hs-model0-lc11-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc11-num-all-failrate}{10.92}
\DefMacro{test-results-hs-model0-lc11-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc11-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc11-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc12-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc12-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc12-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc12-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc12-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc12-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc12-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc12-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc8-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc8-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc8-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc8-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc8-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc8-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc8-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc8-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc6-num-tcs}{144}
\DefMacro{test-results-hs-model0-lc6-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc6-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc6-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc6-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc6-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc6-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc6-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc3-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc3-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc3-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc3-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc3-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc3-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc3-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc3-num-failrate}{0.00}

@@

\DefMacro{test-results-hs-bl-lc9-num-tcs}{100}
\DefMacro{test-results-hs-model0-lc9-num-all-fail}{16,462}
\DefMacro{test-results-hs-model0-lc9-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc9-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc9-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc9-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc9-num-fail}{100}
\DefMacro{test-results-hs-bl-model0-lc9-num-failrate}{100.00}

@@

\DefMacro{test-results-hs-bl-lc7-num-tcs}{111}
\DefMacro{test-results-hs-model0-lc7-num-all-fail}{8,276}
\DefMacro{test-results-hs-model0-lc7-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc7-num-exp-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc7-num-all-failrate}{100.00}
\DefMacro{test-results-hs-model0-lc7-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc7-num-fail}{111}
\DefMacro{test-results-hs-bl-model0-lc7-num-failrate}{100.00}

@@

\DefMacro{test-results-hs-bl-lc5-num-tcs}{140}
\DefMacro{test-results-hs-model0-lc5-num-all-fail}{0}
\DefMacro{test-results-hs-model0-lc5-num-seed-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc5-num-exp-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc5-num-all-failrate}{0.00}
\DefMacro{test-results-hs-model0-lc5-num-pass-to-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc5-num-fail}{0}
\DefMacro{test-results-hs-bl-model0-lc5-num-failrate}{0.00}
\DefMacro{test-results-hs-model1-lc2-num-all-fail}{3,210}
\DefMacro{test-results-hs-model1-lc2-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model1-lc2-num-exp-failrate}{98.34}
\DefMacro{test-results-hs-model1-lc2-num-all-failrate}{98.35}
\DefMacro{test-results-hs-model1-lc2-num-pass-to-fail}{11}
\DefMacro{test-results-hs-bl-model1-lc2-num-fail}{138}
\DefMacro{test-results-hs-bl-model1-lc2-num-failrate}{98.57}
\DefMacro{test-results-hs-model1-lc1-num-all-fail}{3,011}
\DefMacro{test-results-hs-model1-lc1-num-seed-failrate}{97.86}
\DefMacro{test-results-hs-model1-lc1-num-exp-failrate}{97.13}
\DefMacro{test-results-hs-model1-lc1-num-all-failrate}{97.16}
\DefMacro{test-results-hs-model1-lc1-num-pass-to-fail}{30}
\DefMacro{test-results-hs-bl-model1-lc1-num-fail}{136}
\DefMacro{test-results-hs-bl-model1-lc1-num-failrate}{97.14}
\DefMacro{test-results-hs-model1-lc4-num-all-fail}{2,750}
\DefMacro{test-results-hs-model1-lc4-num-seed-failrate}{100.00}
\DefMacro{test-results-hs-model1-lc4-num-exp-failrate}{97.32}
\DefMacro{test-results-hs-model1-lc4-num-all-failrate}{97.45}

@@

\DefMacro{test-results-hs-bl-model1-lc4-num-fail}{132}
\DefMacro{test-results-hs-bl-model1-lc4-num-failrate}{99.25}
\DefMacro{test-results-hs-model1-lc0-num-all-fail}{845}
\DefMacro{test-results-hs-model1-lc0-num-seed-failrate}{95.71}
\DefMacro{test-results-hs-model1-lc0-num-exp-failrate}{88.99}
\DefMacro{test-results-hs-model1-lc0-num-all-failrate}{89.99}
\DefMacro{test-results-hs-model1-lc0-num-pass-to-fail}{19}
\DefMacro{test-results-hs-bl-model1-lc0-num-fail}{134}
\DefMacro{test-results-hs-bl-model1-lc0-num-failrate}{95.71}
\DefMacro{test-results-hs-model1-lc10-num-all-fail}{48,776}
\DefMacro{test-results-hs-model1-lc10-num-seed-failrate}{49.97}
\DefMacro{test-results-hs-model1-lc10-num-exp-failrate}{95.33}
\DefMacro{test-results-hs-model1-lc10-num-all-failrate}{85.79}
\DefMacro{test-results-hs-model1-lc10-num-pass-to-fail}{1,164}
\DefMacro{test-results-hs-bl-model1-lc10-num-fail}{132}
\DefMacro{test-results-hs-bl-model1-lc10-num-failrate}{94.29}
\DefMacro{test-results-hs-model1-lc11-num-all-fail}{46,721}
\DefMacro{test-results-hs-model1-lc11-num-seed-failrate}{49.72}
\DefMacro{test-results-hs-model1-lc11-num-exp-failrate}{95.17}
\DefMacro{test-results-hs-model1-lc11-num-all-failrate}{85.24}
\DefMacro{test-results-hs-model1-lc11-num-pass-to-fail}{1,070}
\DefMacro{test-results-hs-bl-model1-lc11-num-fail}{127}
\DefMacro{test-results-hs-bl-model1-lc11-num-failrate}{95.49}
\DefMacro{test-results-hs-model1-lc12-num-all-fail}{144,823}
\DefMacro{test-results-hs-model1-lc12-num-seed-failrate}{96.71}
\DefMacro{test-results-hs-model1-lc12-num-exp-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc12-num-all-failrate}{96.47}
\DefMacro{test-results-hs-model1-lc12-num-pass-to-fail}{2,804}
\DefMacro{test-results-hs-bl-model1-lc12-num-fail}{136}
\DefMacro{test-results-hs-bl-model1-lc12-num-failrate}{97.14}
\DefMacro{test-results-hs-model1-lc8-num-all-fail}{49,739}
\DefMacro{test-results-hs-model1-lc8-num-seed-failrate}{96.15}
\DefMacro{test-results-hs-model1-lc8-num-exp-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc8-num-all-failrate}{96.42}
\DefMacro{test-results-hs-model1-lc8-num-pass-to-fail}{188}
\DefMacro{test-results-hs-bl-model1-lc8-num-fail}{135}
\DefMacro{test-results-hs-bl-model1-lc8-num-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc6-num-all-fail}{17,212}
\DefMacro{test-results-hs-model1-lc6-num-seed-failrate}{96.40}
\DefMacro{test-results-hs-model1-lc6-num-exp-failrate}{94.91}
\DefMacro{test-results-hs-model1-lc6-num-all-failrate}{94.97}
\DefMacro{test-results-hs-model1-lc6-num-pass-to-fail}{81}
\DefMacro{test-results-hs-bl-model1-lc6-num-fail}{142}
\DefMacro{test-results-hs-bl-model1-lc6-num-failrate}{98.61}
\DefMacro{test-results-hs-model1-lc3-num-all-fail}{5,526}
\DefMacro{test-results-hs-model1-lc3-num-seed-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc3-num-exp-failrate}{95.18}
\DefMacro{test-results-hs-model1-lc3-num-all-failrate}{95.21}
\DefMacro{test-results-hs-model1-lc3-num-pass-to-fail}{56}
\DefMacro{test-results-hs-bl-model1-lc3-num-fail}{135}
\DefMacro{test-results-hs-bl-model1-lc3-num-failrate}{96.43}
\DefMacro{test-results-hs-model1-lc9-num-all-fail}{541}
\DefMacro{test-results-hs-model1-lc9-num-seed-failrate}{3.28}
\DefMacro{test-results-hs-model1-lc9-num-exp-failrate}{3.29}
\DefMacro{test-results-hs-model1-lc9-num-all-failrate}{3.29}
\DefMacro{test-results-hs-model1-lc9-num-pass-to-fail}{51}
\DefMacro{test-results-hs-bl-model1-lc9-num-fail}{1}
\DefMacro{test-results-hs-bl-model1-lc9-num-failrate}{1.00}
\DefMacro{test-results-hs-model1-lc7-num-all-fail}{318}
\DefMacro{test-results-hs-model1-lc7-num-seed-failrate}{2.03}
\DefMacro{test-results-hs-model1-lc7-num-exp-failrate}{3.93}
\DefMacro{test-results-hs-model1-lc7-num-all-failrate}{3.84}
\DefMacro{test-results-hs-model1-lc7-num-pass-to-fail}{20}
\DefMacro{test-results-hs-bl-model1-lc7-num-fail}{2}
\DefMacro{test-results-hs-bl-model1-lc7-num-failrate}{1.80}
\DefMacro{test-results-hs-model1-lc5-num-all-fail}{4,198}
\DefMacro{test-results-hs-model1-lc5-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model1-lc5-num-exp-failrate}{97.57}
\DefMacro{test-results-hs-model1-lc5-num-all-failrate}{97.56}
\DefMacro{test-results-hs-model1-lc5-num-pass-to-fail}{12}
\DefMacro{test-results-hs-bl-model1-lc5-num-fail}{136}
\DefMacro{test-results-hs-bl-model1-lc5-num-failrate}{97.14}
\DefMacro{test-results-hs-model2-lc2-num-all-fail}{3,220}
\DefMacro{test-results-hs-model2-lc2-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model2-lc2-num-exp-failrate}{98.66}
\DefMacro{test-results-hs-model2-lc2-num-all-failrate}{98.65}
\DefMacro{test-results-hs-model2-lc2-num-pass-to-fail}{18}
\DefMacro{test-results-hs-bl-model2-lc2-num-fail}{138}
\DefMacro{test-results-hs-bl-model2-lc2-num-failrate}{98.57}
\DefMacro{test-results-hs-model2-lc1-num-all-fail}{3,067}
\DefMacro{test-results-hs-model2-lc1-num-seed-failrate}{98.57}
\DefMacro{test-results-hs-model2-lc1-num-exp-failrate}{98.99}
\DefMacro{test-results-hs-model2-lc1-num-all-failrate}{98.97}
\DefMacro{test-results-hs-model2-lc1-num-pass-to-fail}{23}
\DefMacro{test-results-hs-bl-model2-lc1-num-fail}{138}
\DefMacro{test-results-hs-bl-model2-lc1-num-failrate}{98.57}
\DefMacro{test-results-hs-model2-lc4-num-all-fail}{2,770}
\DefMacro{test-results-hs-model2-lc4-num-seed-failrate}{97.74}
\DefMacro{test-results-hs-model2-lc4-num-exp-failrate}{98.18}
\DefMacro{test-results-hs-model2-lc4-num-all-failrate}{98.16}
\DefMacro{test-results-hs-model2-lc4-num-pass-to-fail}{9}
\DefMacro{test-results-hs-bl-model2-lc4-num-fail}{133}
\DefMacro{test-results-hs-bl-model2-lc4-num-failrate}{100.00}
\DefMacro{test-results-hs-model2-lc0-num-all-fail}{920}
\DefMacro{test-results-hs-model2-lc0-num-seed-failrate}{97.14}
\DefMacro{test-results-hs-model2-lc0-num-exp-failrate}{98.12}
\DefMacro{test-results-hs-model2-lc0-num-all-failrate}{97.98}
\DefMacro{test-results-hs-model2-lc0-num-pass-to-fail}{22}
\DefMacro{test-results-hs-bl-model2-lc0-num-fail}{136}
\DefMacro{test-results-hs-bl-model2-lc0-num-failrate}{97.14}
\DefMacro{test-results-hs-model2-lc10-num-all-fail}{48,642}
\DefMacro{test-results-hs-model2-lc10-num-seed-failrate}{49.85}
\DefMacro{test-results-hs-model2-lc10-num-exp-failrate}{95.07}
